---
title: "client_rmarkdown"
output: html_document
date: '2022-07-25'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(Microsoft365R)
library(DT)
library(pins)
library(dplyr)

```


# Authentication to Microsoft Azure

```{r}
#tenant = "b721d4a7-5012-49a6-8574-c2d52e59001b"
site_url = "https://rstudioinc.sharepoint.com/sites/integrations-testing"
app="29f4ba1e-3dd5-4f97-a94f-98c68497a9cc"
drive_name = "Documents"
file_src = "penguins_raw.csv"

site <- get_sharepoint_site(site_url = site_url, app=app, auth_type="device_code")

doclib <- site$get_drive()
```

# Downloading file locally and displaying it

Reference: https://cran.r-project.org/web/packages/Microsoft365R/vignettes/od_sp.html

```{r}

# Note the function get_drive() uses drive_id as a parameter (NOT drive name)
drv <- site$get_drive(drive_name)

# Downloading the file:
drv$download_file(src = file_src, dest = "tmp.csv", overwrite = TRUE)

# Reading file into memory (it would be a good idea to have handling here for detecting file type)
data <- read.csv(file="tmp.csv", stringsAsFactors = FALSE, check.names=F)

datatable(data, class = 'cell-border stripe')

```


# Pinning a file / board

Reference: https://pins.rstudio.com/reference/board_ms365.html#ref-examples 

This approach allows for use of Microsoft resources for pinning content. I don't think this allows for access to existing content within Microsoft unless it has been saved using the pin format (so it wouldn't be a good choice for say if users are uploading files to Sharepoint manually and then there is a programmatic script parsing them to reupload an aggregate/analysis). 


```{r}
# Let's connect ms365 as a pinned board. If this folder doesn't already exist it will be created. 
board <- board_ms365(drive = doclib, "general/project1/board")

# Write a dataset as a pin to Sharepoint
board %>% pin_write(iris, "iris", description = "This is a test")

# View the metadat of the pin we just created 
board %>% pin_meta("iris")

# Read a pin
test <- board %>% pin_read("iris")

```



